Exploration

### 2018-03-05 exploration.Rmd
intermediate storage

  #---- Truth: add immigrants
  sdd.j <- which(sdd[,,2,]==sdd.i, arr.ind=TRUE)[,3]
  p.ij <- sdd[,,1,sdd.j][sdd[,,2,sdd.j]==sdd.i]
  Fs[z.i,z.i,i] <- Fs[z.i,z.i,i] + 
    Reduce(`+`, map2(sdd.j, p.ij, 
                     ~h*outer(y, y, calc_rcrImm, p=p, .y, n_seedz=n_seedz,
                              n_flz=n_flz, X.seed=X_seed[.x,], X.fl=X_fl[.x,])))
  Fs[1,z.i,i] <- Fs[1,z.i,i] + 
    Reduce(`+`, map2(sdd.j, p.ij,
                     ~calc_ImmSB(y, p=p, .y, n_seedz=n_seedz, n_flz=n_flz,
                                 X.seed=X_seed[.x,], X.fl=X_fl[.x,])))

@@

########
## plots
########
ggplot(lam.df, aes(x=lon, y=lat, fill=log(lambda))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=lambda>1)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=B1>B0)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd*p$p_emig > D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd*(1-p$p_emig) > D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd*(1-p$p_emig) < D & lambda < 1)) +
  geom_tile()
par(mfrow=c(2,2))
plot(log(lambda) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ pOth, data=lam.df); abline(h=0, col="red", lty=2)
plot(density(log(lam.df$lambda))); abline(v=0, col="red", lty=2)

>>>>

  #---- Truth: add immigrants
  sdd.j <- which(sdd[,,2,]==sdd.i, arr.ind=TRUE)[,3]
  p.ij <- sdd[,,1,sdd.j][sdd[,,2,sdd.j]==sdd.i]
  imm.rcr <- map2(sdd.j, p.ij, 
                     ~h*outer(y, y, calc_rcrImm, p=p, .y, n_seedz=n_seedz,
                              n_flz=n_flz, X.seed=X_seed[.x,], X.fl=X_fl[.x,]))
  Fs[z.i,z.i,i] <- Fs[z.i,z.i,i] + Reduce(`+`, imm.rcr)
  imm.sb <- map2(sdd.j, p.ij,
                     ~calc_ImmSB(y, p=p, .y, n_seedz=n_seedz, n_flz=n_flz,
                                 X.seed=X_seed[.x,], X.fl=X_fl[.x,]))
  Fs[1,z.i,i] <- Fs[1,z.i,i] + 
    Reduce(`+`, imm.sb)

@@

########
## plots
########
ggplot(lam.df, aes(x=lon, y=lat, fill=log(lambda))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
ggplot(lam.df, aes(x=lon, y=lat, fill=lambda>1)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=B1>B0)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd*p$p_emig > D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd*(1-p$p_emig) > D)) + geom_tile()
ggplot(lam.df, aes(x=lon, y=lat, fill=nSd*(1-p$p_emig) < D & lambda < 1)) +
  geom_tile()
par(mfrow=c(2,2))
plot(log(lambda) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambda) ~ pOth, data=lam.df); abline(h=0, col="red", lty=2)
plot(density(log(lam.df$lambda))); abline(v=0, col="red", lty=2)
